Robust Control of a Fluxonium Qubit

### 2020-12-10 paper/3fluxonium.tex
added todo in constraint section

We impose constraints that
reflect the physical limitations of the apparatus and 
improve the experimental realization of the control pulse.
The discrete dynamics \eqref{eq:dyn_con} integrates the states
according to the TDSE \eqref{eq:tdse} and the
fluxonium Hamiltonian \eqref{eq:hamiltonian}
and integrates the moments of the flux amplitude.
Exposing lower order moments of the flux amplitude allows us to penalize their norms
in \eqref{eq:costfun}, smoothing the flux amplitude
and mitigating AWG ringing due to high frequency transitions.
We ensure the desired gate is achieved by imposing the constraints
\eqref{eq:istate_con} and \eqref{eq:tstate_con}.
The initial states in \eqref{eq:istate_con}
are chosen to span the Hilbert space.
The final states in \eqref{eq:tstate_con} are the image
of the initial states under the desired gate.
The ALTRO implementation we use does not currently support complex numbers so
we compute in the isomorphism $\mathcal{H}(\mathbb{C}^{n}) \cong \mathcal{H}(\mathbb{R}^{2n})$
given in \cite{leung2017speedup},
\begin{equation}
  H \ket{\psi} \cong \begin{bmatrix} H_{\textrm{re}} & -H_{\textrm{im}}
    \\ H_{\textrm{im}} & H_{\textrm{re}}\end{bmatrix}
  \begin{bmatrix} \psi_{\textrm{re}} \\ \psi_{\textrm{im}}\end{bmatrix}
  \label{eq:isomorphism}
\end{equation}
We ensure the solver does not take advantage of discretization
error by imposing the normalization constraint \eqref{eq:statenorm_con}.
The constraint \eqref{eq:icintd_con} is an initial condition.
We ensure the pulse has zero net flux by imposing \eqref{eq:znf_con},
which mitigates the hysteresis ubiquitous in flux bias lines
\cite{battistel2019fast, krantz2019quantum, zhang2020universal}.
We ensure gates may be concatenated arbitrarily without
inducing AWG ringing due to high-frequency transitions by imposing
the boundary condition \eqref{eq:concat_con}.
Finally, we ensure the two-level
approximation \eqref{eq:hamiltonian} remains valid
by imposing the amplitude constraint \eqref{eq:amp_con}.
All of the gates presented in this work achieve a maximum
individual constraint violation of $10^{-8}$
for \eqref{eq:dyn_con}--\eqref{eq:amp_con}.

>>>>

\todo{Ask Brian to review this paragraph and the constraints \eqref{eq:dyn_con}-\eqref{eq:amp_con}.
  Is it okay if I have multiple constraints on the same line? The constraints that are on the same
  line are imposed for similar reasons, which makes the list shorter and it easier to reference them here.}
We impose constraints that
reflect the physical limitations of the apparatus and 
improve the experimental realization of the control pulse.
The discrete dynamics \eqref{eq:dyn_con} integrates the states
according to the TDSE \eqref{eq:tdse} and the
fluxonium Hamiltonian \eqref{eq:hamiltonian}
and integrates the moments of the flux amplitude.
Exposing lower order moments of the flux amplitude allows us to penalize their norms
in \eqref{eq:costfun}, smoothing the flux amplitude
and mitigating AWG ringing due to high frequency transitions.
We ensure the desired gate is achieved by imposing the constraints
\eqref{eq:istate_con} and \eqref{eq:tstate_con}.
The initial states in \eqref{eq:istate_con}
are chosen to span the Hilbert space.
The final states in \eqref{eq:tstate_con} are the image
of the initial states under the desired gate.
The ALTRO implementation we use does not currently support complex numbers so
we compute in the isomorphism $\mathcal{H}(\mathbb{C}^{n}) \cong \mathcal{H}(\mathbb{R}^{2n})$
given in \cite{leung2017speedup},
\begin{equation}
  H \ket{\psi} \cong \begin{bmatrix} H_{\textrm{re}} & -H_{\textrm{im}}
    \\ H_{\textrm{im}} & H_{\textrm{re}}\end{bmatrix}
  \begin{bmatrix} \psi_{\textrm{re}} \\ \psi_{\textrm{im}}\end{bmatrix}
  \label{eq:isomorphism}
\end{equation}
We ensure the solver does not take advantage of discretization
error by imposing the normalization constraint \eqref{eq:statenorm_con}.
The constraint \eqref{eq:icintd_con} is an initial condition.
We ensure the pulse has zero net flux by imposing \eqref{eq:znf_con},
which mitigates the hysteresis ubiquitous in flux bias lines
\cite{battistel2019fast, krantz2019quantum, zhang2020universal}.
We ensure gates may be concatenated arbitrarily without
inducing AWG ringing due to high-frequency transitions by imposing
the boundary condition \eqref{eq:concat_con}.
Finally, we ensure the two-level
approximation \eqref{eq:hamiltonian} remains valid
by imposing the amplitude constraint \eqref{eq:amp_con}.
All of the gates presented in this work achieve a maximum
individual constraint violation of $10^{-8}$
for \eqref{eq:dyn_con}--\eqref{eq:amp_con}.
